Results visualization across sites

### 2021-11-17 metanalysis_visualization/visualization.Rmd
added visualization aggregated by country

```{r}
ratios_patients_with_without_psy_all_country <- left_join( ratios_patients_with_without_psy_all, country_map )
ratios_patients_with_without_psy_all_country %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date )  %>%
  ggplot(aes(x = time_p, y = percentage, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(country~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage: patients with psychiatric conditions / total number of patients ( per ", time_period,")"))
```

@@

```{r}
ratios_patients_with_without_psy_all_country %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot(aes(x = time_p, y = ratio, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(country~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Ratio patient with vs without psychiatric conditions ( per ", time_period,")"))
```

>>>>

#### Showing each independent site 
```{r}
ratios_patients_with_without_psy_all_country <- left_join( ratios_patients_with_without_psy_all, country_map )
ratios_patients_with_without_psy_all_country %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date )  %>%
  ggplot(aes(x = time_p, y = percentage, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(country~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage: patients with psychiatric conditions / total number of patients ( per ", time_period,")"))
```

#### Aggregating the sites in each country

```{r}
ratios_patients_with_without_psy_all_country <- left_join( ratios_patients_with_without_psy_all, country_map )

ratios_patients_with_without_psy_aggregated <- ratios_patients_with_without_psy_all_country %>%
  group_by( time_p, country ) %>%
  mutate( no_psy = sum( count_no_psy_patients ), 
          psy = sum( count_psy_patients ), 
          total = sum(count_no_psy_patients) + sum(count_psy_patients), 
          ratio_by_country = psy / no_psy, 
          perc_by_country = 100*(psy / total) ) %>%
  select( time_p, no_psy, psy, total, ratio_by_country, perc_by_country, country)

ratios_patients_with_without_psy_aggregated %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=perc_by_country, 
              group = country, color = country))+
  geom_point( aes(shape=country, color=country) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_colour_viridis_d() +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle(paste0("Percentage: patients with psychiatric conditions / total number of patients ( per ", time_period,") \n (aggregated by country)")) +
    xlab("period (months)") +
    ylab("percentage (%)")
```

@@

#### Showing each site per country 
```{r}
ratios_patients_with_without_psy_all_country %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot(aes(x = time_p, y = ratio, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(country~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Ratio patient with vs without psychiatric conditions ( per ", time_period,")"))
```

#### Aggregating the values of the sites per country

```{r}
ratios_patients_with_without_psy_aggregated %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=ratio_by_country, 
              group = country, color = country))+
  geom_point( aes(shape=country, color=country) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_colour_viridis_d() +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Ratios: patients with psychiatric conditions / without psychiatric conditions \n (aggregated by country)") +
    xlab("period (months)") +
    ylab("ratio")
```
